Co-operation between the sexes trumps selfish control of female meiotic drive. Or Sperm do not evolve to collaborate in female meiotic drive. Or Why does female meiosis allow the opportunity for exploitation by selfish sperm?

### 2014-02-04 writeup_and_notes/male_dependent_drive.tex
redid figures for paper

Despite the apparent unity of the organism, alleles can
gain an evolutionary advantage at a cost to  individual fitness
\citep{Burt2006}, often by exploiting meiosis and gametogensis.
Because only one of the four products of female meiosis is transmitted to the egg, female meiosis is particularly vulnerable to such exploitation \citep{Sandler1957,Pardo-ManuelDeVillena2001a}. 
An allele that biases female meiosis in its favor (i.e. a meiotic driver), may increase in frequency even if this driver entails a pleiotropic fitness cost \citep{Prout1973}, generating a genetic conflict between the success of the driver and organismal fitness.
Meiotic drivers observed in nature (in both plants
\citep{Buckler1999,Fishman2005,Fishman2008}, and animals
\citep{Agulnik1990,Wu2005,Pardo-ManuelDeVillena2001c}) highlight this
conflict -- the selfish benefits of drive and the associated
pleiotropic fitness costs sustain a balanced polymorphism
\citep{Prout1973}, 
and often generate an ongoing evolutionary escalation of drive suppressors and enhancers \citep{Dawe1996,Fishman2008}. 
The threat of meiotic drive to organismal fitness is potentially so
severe that many basic properties of
meiosis and o\"{o}genesis, including the initial genome doubling in
meiosis I \citep{Haig1991}, arrested female meiosis
\citep{Mira1998}, centromere machinery \citep{MalikHenikoff}, and sex differences in the recombination rate \citep{Haig2010,Brandvain2012} 
have perhaps evolved to disrupt meiotic drive and enforce fairness.

@@

It is also not the case that sperm is mechanistically incapable of influencing the outcome of female meiosis.
Mechanistic evidence for this possibility comes from
\emph{C. elegans} the fact that premature deployment of the aster (a vital component of mitotic
machinery) provided by the sperm can disrupting MII meiotic segregation
in the egg, leading to a triploid zygote \citep{McNally2012}. 
Additionally, genetic evidence suggests that the transmission patterns
in heterozygous females many potentially depend on sperm haplotype. 
Specifically, the two best characterized female meiotic drive systems in mouse (In and Om), both operate by distorting the second meiotic division, 
and in both systems the outcome of female meiosis depends the genotype of the fertilizing sperm \citep{Agulnik1993,Wu2005}. 
While such genetic evidence is suggestive, we note the difficulty in ruling out the alternative hypothesis of early selection    \citep[Give page numbers to discussion of this in][]{Burt2006}.

@@

We first consider a driving allele neutral in heterozygotes, 
	but deleterious in homozygotes (whose relative fitness is $1-s$) \yb{(EQUATIONS A3-A4)}.  
In this model, a standard meiotic driver can always invade because 
	when rare it occurs predominantly in heterozygotes and it therefore drives without a fitness cost. 
However, a severe homozygous fitness cost ($s>XXd$) prevents  
	drivers from fixing  \citep{Prout1973}, 
	providing an opportunity for the evolution of
	drive suppressors \citep{XX}, corresponding well to 
	empirical examples of female meiotic drive.

@@

When a deleterious recessive self-promoting driver does spread, 
	it spends much time at low frequency, because when rare it is unlikely to meet a complimentary sperm. 
However, once relatively common, a self-promoting driver spreads rapidly to fixation due to its
	positive frequency dependent behavior (Inset in Figure \ref{Invasion_space}).  
This lack of a balanced polymorphism precludes the evolution of an allele that suppresses this form of meiotic drive.
\yb{POINT TO SOME MATHS OR FIGURE}

Inclusion of a heterozygous fitness cost (e.g. additive fitness cost) further constrains the evolution of a self-promoting driver. 
While a  standard female  driver invades from low frequency when the transmission advantage outweighs the fitness cost (XXX),
	a rare self-promoter pays a fitness cost, but drives only weakly because complementary sperm are uncommon. 
This frequency independent fitness cost, and positive frequency dependent drive generates a bistable system. 
Below a cutoff frequency the self-promoter driver deterministically decreases in frequency 
	because it pays the  heterozygous fitness cost  but drives ineffectively (see FigureS\ref{bistable_additive}). 
Above this frequency, the allele increases deterministically because the commonness of complementary sperm 
	make drive effective enough to overcome the associated fitness cost.
This bistability prevents self-promoting drivers from invading 	
	reasonably sized populations, and assures that if they do invade they will rapidly fix.
\yb{Our model therefore predicts that self-promoting drivers will not be observed as polymorphisms in natural populations. }

While the allelic identity of sperm could plausibly influence the outcome of female meiosis, 
	limited gene expression in sperm \citep[e.g.][]{Joseph2004}
	suggest a model where sperm influence female meiosis via expression of the fertilizing male's
	diploid genotype (perhaps due to proteins and RNAs packaged into the sperm).
This adds an additional parameter to the system -- the dominance of the drive enhancer in heterozygous males, 
	when this dominance is high, a narrow sliver of parameter space sustaining a polymorphism emerges (see Figure S\ref{Effect_of_dominance})
 	\yb{presumably because positive frequency dependence diminishes with the dominance of the male effect driver.}

@@

\begin{figure}
	\rotatebox{270}{\includegraphics[width = 0.8
          \textwidth]{Figures/sperm_egg_cartoon1.ps}}
\caption{transmission probabilities for alleles through female
  meiosis depend on sperm genotype. 2 allele model}  
\label{Eggsperm_2_allele_cartoon}
\end{figure}

\begin{figure}
\includegraphics[width = 0.8 \textwidth]{Figures/invasion_space_recessive_driver.eps}
\caption{Invasion analysis. Likely merge with Figure 1. \yb{PERHAPS COMPARE TO TRADITIONAL DRIVER IN THIS FIGURE} } \label{Invasion_space}
\end{figure}

@@

\begin{figure}
	\rotatebox{270}{\includegraphics[width = 0.8
          \textwidth]{Figures/sperm_egg_cartoon2.ps}}
\caption{transmission probabilities righthand allele through female
  meiosis}  \label{Eggsperm_3_allele_cartoon}
\end{figure}

\begin{figure}
\includegraphics[width = 0.8 \textwidth]{Figures/trajectories_of_sperm_based_supressors.eps} 
\caption{Trajectories of two sperm-based supressors of drive. Possibly
merge this figure the 3 allele cartoon}  \label{Trajectories_of_supressors}
\end{figure}

@@

Above, we explored a model were a driver that drove in females when signaled by a complementary allele in sperm.  
We complement this single locus model  of pleiotropy with an alternative model of two linked loci - one female driver and the other a sperm allele which modifies the effect of drive upon fertilization. 
%Here, we examine an alternative scenario (and more realistic) in which
In this model initially a female meiotic driver, with no sperm-dependency, reaches drive-viability equilibrium (with two alleles
$A$ and $B$ are the ancestral non-driver and driver alleles).
Subsequently, a sperm-acting modifier of female meiotic drive arises tightly
        linked to this balanced locus (effectively creating a third
        allele/haplotype at this locus).
Assuming tight linkage between female driver and sperm modifier is consistent with the nature of well characterized meiotic drive systems 
	which are often maintained as polymorphic inversions with numerous linked modifiers (CITE).

@@

%%%sperm-acting drive suppressors
While  sperm enhancement of a female drive cannot displace a polymorphic female driver, sperm based drive suppression - 
	that is sperm-acting alleles that act to restore  fairness of female meiosis can. 
If these sperm-acting drive suppressors arise on
	the non-driving $A$ background (creating a third allele $A^{-}$) ;
	or are unlinked to the drive locus they readily invade a population segregating
	for the drive system ($AB$, see Figure). 
This allele lowers the frequency of the original drive system (perhaps to zero),
	and spreads to fixation if it does not carry strong fitness costs
	(Figure \ref{Eggsperm_3_allele_cartoon} and \ref{Trajectories_of_supressors}A). 
\yb{This result is consistent with previous work showing that drive suppressors unlinked to, or in repulsion phase with drivers usually invade polymorphic drive systems \citep[e.g. ][]{Brandvain2012}.}

@@

\gc{Do we mention the In and Om locus here or in the discussion as a
	 potential e.g. Do we mention the fact that the frequency of these
	 newly invade sperm dodging alleles can be lower than the original system?}\\

@@

%Our results provide a plausible answer to why female oogenesis and meiosis has
%not evolved to prevent sperm alleles from hijacking . 
%Such self-promoting sperm alleles are usually prevented from 
%entering the population if they have fitness costs, and are not
%maintained as polymorphisms if they do. As such, these type of
%exploitation can not drive sustained genetic conflict and so it is unlikely
%that female oogenesis and meiosis will evolve to prevent their effect.

@@

It seems that allowing sperm to influence the outcome of meiosis would generate a confluence of these potential conflicts -- 
	sperm could actually assist an allele that distorts female meiosis.
However, this is not the case.
We find that an allele which acts through sperm to distort female meiosis in its favor %YB [too awkward / unclear?] 
	can rarely spread through a population if it bears any cost. 
Additionally, when this self-promoting driver can spread, it can only rarely 
	be maintained as a protected polymorphism, and due to its positive frequency dependence 
	it spends very little time at intermediate frequency.
As such, this type of exploitation cannot generate a sustained genetic conflict and so it is unlikely
	that female oogenesis and meiosis will evolve to prevent their effect.  
This likely explains why females can delay the completion of meiosis until after fertilization 
	without risking exploitation by collaborations by female
        drivers and sperm alleles.
%Male modification of recombination rates. \yb{trying to think through this \dots{}}

Why is it that an allele that biases female meiosis in its favor can generate a genetic conflict, but an allele in sperm that assists this female driver cannot? 
So long as the transmission advantage of female meiotic drive outweigh the organismal fitness cost to heterozygotes the female driver can spread when rare, and it increases in 		
	frequency until the fitness cost experienced when homozygous balances the transmission advantage.
By contrast a sperm promotor of female drive is only effective when matched with a heterozgyote female -- meaning that when rare this allele rarely enhances female drive. 
Even worse, when it does so it will preferentially find itself in a low fitness drive homozygote. 
Not only are drive-promoting sperm alleles unable to create a sustained genetic conflict, 
	but alleles in sperm with the opposite effect - that is those that prevent their own drive through female meiosis do maintain a polymorphisms and 
	provide evolution  with time and opportunity to further minimize drive.
This is because such drive suppressing alleles reduced their chances of forming  low fitness homozygotes.
In fact, an allele in sperm which causes the alternate allele to drive can be favored (FIG), a counterintuitive result 
	consistent with the tenuous evidence that the non-driving
        $ln^-$ allele is over transmitted when fertilized by $ln^+$
        sperm \cite{agulnick, Pomiankowski1993}.

\yb{DOES THIS GO ANYWHERE? }

Males can potentially influence the outcome of meiosis even before fertilization. 
For example in Drosophila and other taxa, sperm accessory
        gland proteins (ACPs) increase the female recombination rate
        \cite{SOMEthING}, and there is some evidence that there is
        variance across male genotypes in there effect on female
        recombination rate \cite{Stevison2012}.
Presumably this is a pleiotropic consequence of the resolution of double strand breaks initiated by the stressful/toxic composition of ACPs. 
However, a pleiotropic effect of this is to increase the recombination rate which can decrease the effectiveness of female meiotic drivers
active during MI \citep{Brandvain}. 
We speculate that other effects of sperm on female meiosis may also be tolerated by females as a way of ensuring meiotic fairness -- 
	that is females evolve to allow male influence on female meiosis in cases in which the male influence is  egalitarian.

@@

Therefore, the interests of fertilizing sperm and female are quite well aligned during syngamy -- producing a viable and potentially fit offspring. 
%As noted above there are even opportunities for coevolution between sperm-based suppressors of female meiotic drive and the female genome.
Thus it seems plausible that aspects of oogenesis may actively evolve to facilitate the influence of sperm on ensuring a fair  outcome of female meiosis which generates fit offspring.
In light of that it is interesting to consider whether the phylogenetic variation in the stage of oogenesis when fertilization takes place reflects not
	only species' different reproductive ecologies, but also different selection pressures shaping the interaction of sperm alleles with female meioses. 
\\
\\
\\
\\
\gc{Other pointsf}\\
\\
\\
\gc{Add short paragraph about sex chromosomes here? XY systems don't care. ZW systems (males ZZ, females ZW). If there is
sex ratio distortion how could this play out?}

POssibility that this could happen in plants if pollen emit signals to ``egg''
Discussion of OM and IN.

>>>>

Despite the apparent unity of the organism, alleles can
gain an evolutionary advantage at a cost to  individual fitness
\citep{Burt2006}, often by exploiting meiosis and gametogenesis.
Because only one of the four products of female meiosis is transmitted to the egg, female meiosis is particularly vulnerable to such exploitation \citep{Sandler1957,Pardo-ManuelDeVillena2001a}. 
An allele that biases female meiosis in its favor (i.e. a meiotic driver), may increase in frequency even if this driver entails a pleiotropic fitness cost \citep{Prout1973}, generating a genetic conflict between the success of the driver and organismal fitness.
Meiotic drivers observed in nature (in both plants
\citep{Buckler1999,Fishman2005,Fishman2008}, and animals
\citep{Agulnik1990,Wu2005,Pardo-ManuelDeVillena2001c}) highlight this
conflict -- the selfish benefits of drive and the associated
pleiotropic fitness costs sustain a balanced polymorphism
\citep{Prout1973}, 
and often generate an ongoing evolutionary escalation of drive suppressors and enhancers \citep{Dawe1996,Fishman2008}. 
The threat of meiotic drive to organismal fitness is potentially so
severe that many basic properties of
meiosis and o\"{o}genesis, including the initial genome doubling in
meiosis I \citep{Haig1991}, arrested female meiosis
\citep{Mira1998}, centromere machinery \citep{MalikHenikoff}, and sex differences in the recombination rate \citep{Haig2010,Brandvain2012} 
have perhaps evolved to disrupt meiotic drive and enforce fairness.

@@

It is also not the case that sperm is mechanistically incapable of influencing the outcome of female meiosis.
Mechanistic evidence for this possibility comes from
\emph{C. elegans} the fact that premature deployment of the aster (a vital component of mitotic
machinery) provided by the sperm can disrupting MII meiotic segregation
in the egg, leading to a triploid zygote \citep{McNally2012}. 
Additionally, genetic evidence suggests that the transmission patterns
in heterozygous females many potentially depend on sperm haplotype. 
Specifically, two female meiotic drive systems in mouse (In and Om), both operate by distorting the second meiotic division, 
and in both systems the outcome of female meiosis depends the genotype of the fertilizing sperm \citep{Agulnik1993,Wu2005}. 
While such genetic evidence is suggestive, we note the difficulty in
ruling out the alternative hypothesis of early selection on zygotes \citep[pages
52-54][]{Burt2006}.

@@

We first consider a driving allele neutral in heterozygotes, 
	but deleterious in homozygotes (whose relative fitness is
        $1-s$). This model is laid out in eqn. \ref{eqn.A1}-\ref{eqn.A3}.
In this model, a standard meiotic driver can always invade because 
	when rare it occurs predominantly in heterozygotes and it therefore drives without a fitness cost. 
However, a severe homozygous fitness cost ($s>XXd$) prevents  
	drivers from fixing  \citep{Prout1973}, 
	providing an opportunity for the evolution of
	drive suppressors \citep{XX}, corresponding well to 
	empirical examples of female meiotic drive.

@@

When a deleterious recessive self-promoting driver does spread, 
	it spends much time at low frequency, because when rare it is unlikely to meet a complimentary sperm. 
However, once relatively common, a self-promoting driver spreads rapidly to fixation due to its
	positive frequency dependent behavior (Inset in Figure \ref{Invasion_space}).  
This lack of a balanced polymorphism ( Figure \ref{Invasion_space}) precludes the evolution of an
allele that suppresses this form of meiotic drive in females.
\yb{POINT TO SOME MATHS OR FIGURE}

Inclusion of a heterozygous fitness cost (e.g. additive fitness cost) further constrains the evolution of a self-promoting driver. 
While a standard female driver invades from low frequency when the transmission advantage outweighs the fitness cost (XXX),
	a rare self-promoter pays a fitness cost, but drives only weakly because complementary sperm are uncommon. 
This frequency-independent fitness cost, and positive frequency dependent drive generates a bistable system. 
Below a cutoff frequency the self-promoter driver deterministically decreases in frequency 
	because it pays the  heterozygous fitness cost  but drives
        ineffectively (see Figure S\ref{bistable_additive}). 
Above this frequency, the allele increases deterministically because the commonness of complementary sperm 
	make drive effective enough to overcome the associated fitness cost.
This bistability prevents self-promoting drivers from invading 	
	reasonably sized populations, and assures that if they do invade they will rapidly fix.
Our model therefore predicts that self-promoting drivers will not be observed as polymorphisms in natural populations.

While the allelic identity of sperm could plausibly influence the outcome of female meiosis, 
	limited gene expression in sperm \citep[e.g.][]{Joseph2004}
	suggest a model where sperm influence female meiosis via expression of the fertilizing male's
	diploid genotype (perhaps due to proteins and RNAs packaged into the sperm).
This adds an additional parameter to the system -- the dominance of the drive enhancer in heterozygous males, 
	when this dominance is high, a narrow sliver of parameter space sustaining a polymorphism emerges (see Figure S\ref{Effect_of_dominance})
 presumably because positive frequency dependence diminishes with the dominance of the male effect driver.

@@

\begin{figure}
	\rotatebox{90}{
\includegraphics[width = 0.5
          \textwidth]{Figures/Sperm_egg_cartoon_paper_Fig1.eps}}
\caption{transmission probabilities for alleles through female
  meiosis depend on sperm genotype. 2 allele model}  
\label{Eggsperm_2_allele_cartoon}
\end{figure}

\begin{figure}
\includegraphics[width = 0.8 \textwidth]{Figures/invasion_space_recessive_driver.eps}
\caption{Invasion analysis for a female meiotic drive allele with
  recessive costs. First consider a simple female meiotic
  drive system, where the allele is transmitted a fraction $d>1/2$ of
  meioses in female heterozygotes, inspective
  of the allele carried by the fertilizing sperm. Such an allele can
  invade over all of the parameter space, and will be maintained as a
  protected polymorphism in the white region, and can fix in the
  population in all of the parameter space colored green,
  and will fix  or orange. Now consider an allele that is fairly transmitted through
  female meiosis when fertilized by a sperm carrying a different
  allele, but a fraction $d>1/2$ when a heterozygote egg is fertilized
  by a sperm carrying the allele (as depicted in Figure
  \ref{Eggsperm_2_allele_cartoon}). Such an allele can only invade in
  the region of parameter space colored orange, and it fixes over all
  of this parameter region. 
 In the inset we show trajectories of sperm-dependent female drive
 alleles that can invade the population, each allele has $s =0.1$ against the
 homozygotes and $d =0.6$, $0.7$, $0.8$ shown in yellow, blue, and red. 
 \gc{Likely make this Figure 1B.} } \label{Invasion_space}
\end{figure}

@@

\begin{figure}
	\rotatebox{90}{\includegraphics[width = 0.8
          \textwidth]{Figures/Sperm_egg_cartoon_paper_Fig2.eps}}
\caption{Transmission probabilities righthand allele through female
  meiosis}  \label{Eggsperm_3_allele_cartoon}
\end{figure}

% \begin{figure}
% \includegraphics[width = 0.8 \textwidth]{Figures/trajectories_of_sperm_based_supressors.eps} 
% \caption{Trajectories of two sperm-based supressors of drive. Possibly
% merge this figure the 3 allele cartoon}  \label{Trajectories_of_supressors}
% \end{figure}

@@

Above, we explored a model were a driver that drove in females when signaled by a complementary allele in sperm.  
We complement this single locus model of an allele with effects in
both male and with femalr, with  an alternative model of two linked loci - one female driver and the other a sperm allele which modifies the effect of drive upon fertilization. 
%Here, we examine an alternative scenario (and more realistic) in which
In this model initially a female meiotic driver, with no sperm-dependency, reaches drive-viability equilibrium (with two alleles
$A$ and $B$ are the ancestral non-driver and driver alleles).
Subsequently, a sperm-acting modifier of female meiotic drive arises tightly
        linked to this balanced locus (effectively creating a third
        allele/haplotype at this locus).
Assuming tight linkage between female driver and sperm modifier is consistent with the nature of well characterized meiotic drive systems 
	which are often maintained as polymorphic inversions with numerous linked modifiers (CITE).

@@

%%%sperm-acting drive suppressors
While  sperm enhancement of a female drive cannot displace a polymorphic female driver, sperm based drive suppression - 
	that is sperm-acting alleles that act to restore  fairness of female meiosis can. 
If these sperm-acting drive suppressors arise on
	the non-driving $A$ background (creating a third allele $A^{-}$) ;
	or are unlinked to the drive locus they readily invade a population segregating
	for the drive system ($AB$, see Figure). 
This allele lowers the frequency of the original drive system (perhaps to zero),
	and spreads to fixation if it does not carry strong fitness costs
	(Figure \ref{Eggsperm_3_allele_cartoon} and \ref{Trajectories_of_supressors}A). 
This result is consistent with previous work showing that drive suppressors unlinked to, or in repulsion phase with drivers usually invade polymorphic drive systems \citep[e.g. ][]{Brandvain2012}.

@@

%\gc{Do we mention the In and Om locus here or in the discussion as a
%	 potential e.g. Do we mention the fact that the frequency of these
%	 newly invade sperm dodging alleles can be lower than the original system?}\\

@@

@@

It seems that allowing sperm to influence the outcome of female meiosis would generate a confluence of these potential conflicts -- 
	sperm could actually assist an allele that distorts female meiosis.
However, this is not the case.
We find that an allele which acts through sperm to distort female meiosis in its favor %YB [too awkward / unclear?] 
	can rarely spread through a population if it bears any cost. 
Additionally, when this self-promoting driver can spread, it can only rarely 
	be maintained as a protected polymorphism, and due to its positive frequency dependence 
	it spends very little time at intermediate frequency.
As such, this type of exploitation cannot generate a sustained genetic conflict and so it is unlikely
	that female oogenesis and meiosis will evolve to prevent their effect.  
This likely explains why females can delay the completion of meiosis until after fertilization 
	without risking exploitation by collaborations by female
        drivers and sperm alleles.
%Male modification of recombination rates. \yb{trying to think through this \dots{}}

Why is it that an allele that biases female meiosis in its favor can generate a genetic conflict, but an allele in sperm that assists this female driver cannot? 
So long as the transmission advantage of female meiotic drive outweigh the organismal fitness cost to heterozygotes the female driver can spread when rare, and it increases in 		
	frequency until the fitness cost experienced when homozygous balances the transmission advantage.
By contrast a sperm promotor of female drive is only effective when matched with a heterozgyote female -- meaning that when rare this allele rarely enhances female drive. 
Even worse, when it does so it will preferentially find itself in a low fitness drive homozygote. 
Not only are drive-promoting sperm alleles unable to create a sustained genetic conflict, 
	but alleles in sperm with the opposite effect - that is those that prevent their own drive through female meiosis do maintain a polymorphisms and 
	provide evolution  with time and opportunity to further minimize drive.
This is because such drive suppressing alleles reduced their chances
of forming low fitness homozygotes. 
In fact, an allele in sperm which causes the alternate allele to drive can be favored (FIG), a counterintuitive result 
	consistent with the tenuous evidence that the non-driving
        $ln^-$ allele is over transmitted through female meiosis in $ln^-/ln^+$ heterozygote when fertilized by $ln^+$
        sperm \cite{agulnick, Pomiankowski1993}.   
More generally both linked and unlinked alleles may often spread that act through sperm to
reduce the opportunity of female meiotic drive in order to disable
segregating drive systems, by for example reducing the mechanistic
asymmetries that female drivers exploit.

\gc{Is there some nice way to work in green beard ideas}

The interests of fertilizing sperm and female are quite well aligned during syngamy -- producing a viable and potentially fit offspring. 
%As noted above there are even opportunities for coevolution between sperm-based suppressors of female meiotic drive and the female genome.
Thus it seems plausible that aspects of oogenesis may actively evolve to facilitate the influence of sperm on ensuring a fair  outcome of female meiosis which generates fit offspring.
In light of that it is interesting to consider whether the phylogenetic variation in the stage of oogenesis when fertilization takes place reflects not
	only species' different reproductive ecologies, but also different selection pressures shaping the interaction of sperm alleles with female meioses. 
%\gc{Add short paragraph about sex chromosomes here? XY systems don't care. ZW systems (males ZZ, females ZW). If there is
%sex ratio distortion how could this play out?}

%\yb{DOES THIS GO ANYWHERE? }

% Males can potentially influence the outcome of meiosis even before fertilization. 
% For example in Drosophila and other taxa, sperm accessory
%         gland proteins (ACPs) increase the female recombination rate
%         \cite{SOMEthING}, and there is some evidence that there is
%         variance across male genotypes in there effect on female
%         recombination rate \cite{Stevison2012}.
% Presumably this is a pleiotropic consequence of the resolution of double strand breaks initiated by the stressful/toxic composition of ACPs. 
% However, a pleiotropic effect of this is to increase the recombination rate which can decrease the effectiveness of female meiotic drivers
% active during MI \citep{Brandvain}. 
% We speculate that other effects of sperm on female meiosis may also be tolerated by females as a way of ensuring meiotic fairness -- 
% 	that is females evolve to allow male influence on female meiosis in cases in which the male influence is  egalitarian.

@@

\section*{Appendix}
In our first scenerio allele $A$ is the ancestral allele and allele
$B$ is our sperm dependent drive allele.
The sperm dependence of the drive is a form of assortative
transmission (mating), and so we have to keep track of the genotype frequencies.
Our genotype frequencies at birth are $x_{AA},~x_{AB},$ and
$x_{BB}$. These three genotypes have fitnesses $w_{AA},~w_{AB},$ and
$w_{BB}$, which are identical between males and females. As the
fitnesses are the same in males and females the frequencies of the
genotypes are identical in males and females, but in the following
equations they are marked with $\Mars$ and $\Venus$ respectively to
allow the reader to more easily follow the logic.
The frequency of the three genotypes at birth in the next generation is:
\begin{equation}
x'_{BB} =\frac{1}{\bar{w} } \Big( w_{BB} x_{BB}^{\Venus} (w_{BB} x_{BB}^{\Mars} +\frac{1}{2}
  w_{AB} x_{AB}^{\Mars} ) + w_{AB} x_{AB}^{\Venus} (d w_{BB}
  x_{BB}^{\Mars} +\frac{1}{2} d
w_{AB} x_{AB}^{\Mars} ) \Big),  \label{eqn.A1}
\end{equation}
\begin{equation}
x'_{AA} =\frac{1}{\bar{w} } \Big(  w_{AA} x_{AA}^{\Venus} (w_{AA} x_{AA}^{\Mars} + \frac{1}{2}
   w_{AB} x_{AB}^{\Mars}) + w_{AB} x_{AB}^{\Venus}(\frac{1}{2} w_{AA} x_{AA}^{\Mars}+ \frac{1}{2} 
  w_{AB} x_{AB}^{\Mars}) \Big),  \label{eqn.A2}
\end{equation}
and
\begin{eqnarray}
x'_{AB} = & \frac{1}{\bar{w} } \Big( w_{AA} x_{AA}^{\Venus}  ( w_{BB}  x_{BB}^{\Mars} + \frac{1}{2}
  w_{AB}  x_{AB}^{\Mars} ) +w_{BB} x_{BB}^{\Venus} ( w_{AA}  x_{AA}^{\Mars} + \frac{1}{2}
  w_{AB}  x_{AB}^{\Mars} )  \nonumber \\
& + x_{AB}^{\Venus}(\frac{1}{2}  w_{AA}  x_{AA}^{\Mars}+\frac{1}{2} (1-d)
 w_{AB}  x_{AB}^{\Mars} + \frac{1}{4}  w_{AB}
 x_{AB}^{\Mars} + (1-d)  w_{BB}  x_{BB}^{\Mars} ) \Big) \label{eqn.A3}
\end{eqnarray}
where the mean fitness of the population is
\begin{equation}
\bar{w} = w_{AA} x_{AA}+w_{AB}  x_{AB} +w_{BB}  x_{BB}.
\end{equation}
